Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-12-07 paperDraft3.tex
fixed abstract

\begin{abstract}
    We use a Bayesian hierarchical model to assess the reliability of the Joint
    Light Tactical Vehicle (JLTV), which is a family of vehicles. The proposed
    model effectively combines information across three phases of testing and
    across common vehicle components. The analysis yields estimates of failure
    rates for specific failure modes and vehicles as well as an overall estimate
    of the failure rate for the family of vehicles. We are also able to obtain
    estimates of how well vehicle modifications between test phases improve
    failure rates. In addition to using all data to improve on current
    assessments of reliability and reliability growth, we illustrate how to
    leverage the information learned from the three phases to determine
    appropriate specifications for subsequent testing that will demonstrate if
    the reliability meets a given reliability threshold.
\end{abstract}

>>>>

\begin{abstract}
    We use a Bayesian hierarchical model to assess the reliability of a family
    of vehicles. The proposed model effectively combines information across
    three phases of testing and across common vehicle components. The analysis
    yields estimates of failure rates across failure modes and vehicles as well
    as an overall estimate of the failure rate for the family of vehicles. We
    are also able to obtain estimates of the Fix Effectiveness Factor (FEF), a
    measure of how well repairs between test phases improve failure rates. In
    addition to using all data to improve on current assessments of reliability
    and reliability growth, we illustrate how to leverage the information
    learned from the three developmental test phases to determine the length of
    testing needed to demonstrate a given reliability threshold in the next
    testing phase.
\end{abstract}
